Reliable feature point matching

### 2013-08-02 text/thesis.tex
Added thesis and changes to bibliography

\documentclass[conference]{IEEEtran}
%\documentclass{article}
\usepackage{footnote}
%\usepackage[font={small}]{caption}
%\usepackage{sidecap}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
%\usepackage[stable]{footmisc}
%\usepackage{caption}
%\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\title{Mirror Match: Reliable Feature Point Matching Without Geometric Constraints}
\author{Anonymous ACPR Submission}

\maketitle
%
\begin{abstract}
Many algorithms have been proposed to solve the problem of matching 
feature points in two or more images using geometric assumptions to 
increase the robustness of the matching. However, very little work 
addresses the case where these assumptions might not hold. In particular 
few methods address the problem of reliable matching in cases where it 
is unknown whether two images have any corresponding areas or objects in 
the first place.

We propose two algorithms for matching feature points without the use of 
geometric constraints. The first relies on the fact that any match 
between two images should be better than all possible matches within a 
single image. The second algorithm extends this idea by using community 
structure in the similarity graph of feature points to find reliable 
correspondences. To evaluate the algorithms experimentally, we introduce 
a simple method to generate a large amount of test cases based on a set 
of image pairs with viewpoint changes. Our results show that the 
proposed algorithm is generally superior to traditional approaches in 
finding correct correspondences.
\end{abstract}
\section{Introduction}
When matching feature points between two or more images we are often 
faced with the problem of correctly identifying the actual 
correspondences among many possible pairings. Several methods have been 
proposed in the literature to solve this problem. Many approaches look 
at the geometric configuration of feature points and match them based on 
various assumptions about the geometric relationship between the images. 
These assumptions are then used to create different constraints on the 
matches, e.g.\ angular constraints \cite{kim2008efficient}, epipolar 
constraints \cite{torr2000mlesac,chum2005matching}, or pairwise 
constraints \cite{choi2009robust,leordeanu2005spectral}.
%When matching feature points between two or more images we are often 
%faced with the problem of correctly identifying the actual 
%correspondences among many possible pairings. Several methods have been 
%proposed in the literature to solve this problem. In particular many 
%approaches look at the geometric configuration of the feature points 
%and match them according to assumptions made about the geometric 
%relationship between the images matched. A simple example would be to 
%only consider matches that aren't   too much with respect to the 
%average angle and distancen as considered by \cite{kim2008efficient}.  
%This performs well in situations where no camera rotation occurs 
%between the two images, but fails when this assumption isn't met. 
%Various scenarios have been proposed to improve on this simple 
%assumption such as epipolar constraints (\cite{torr2000mlesac}, 
%\cite{chum2005matching}) and pairwise constraints 
%(\cite{choi2009robust}, \cite{leordeanu2005spectral}). The Epipolar 
%constraint carries the assumption that the two images matched are 
%related by an affine transformation. That is, there is no relative 
%movement of objects in between images and either the viewpoint is fixed 
%or the image resides entirely on a plane. In practice this assumption 
%largely holds true when all objects we are interested in matching are 
%roughly the same distance from the camera and when we expect to match 
%objects that are consistently positioned across images.  Pairwise 
%constraints provide a more robust approach to the same problem by 
%looking at a set of proposed correspondences and defining a pairwise 
%error between any two matches for example based on the assumption that 
%two neighboring correspondences will usually have similar angles and 
%distances. We can then convert the problem to an optimization problem 
%and return a set of correspondences that minimizes this error such as 
%proposed in \cite{choi2009robust} and \cite{leordeanu2005spectral}.  
%This approach provides more robustness in cases where assumptions that 
%are violated globally still hold on a local scale.
An alternative is to pick out different areas in each image and pair 
areas when correspondence pairs are mainly found going from one area to 
another. This allows for the filtering of all correspondences that do 
not fall within paired areas. Examples include \emph{Isodata} 
\cite{das2008event}, which clusters feature points according to their 
position in the image, and the method from \cite{wu2011robust}, which 
uses maximally stable extremal regions (MSER) feature points to 
designate areas. In this paper the algorithm from \cite{das2008event} 
will later be referred to as \emph{Isodata}.

%proposes clustering feature points by using their geometric position 
%and exclude correspondences that are geometrically deviant. A more 
%sophisticated approach is introduced in \cite{wu2011robust} where the 
%areas are created by using the MSER feature detector to find areas of 
%interest in the images. These areas can be defined as an ellipse with a 
%certain radius around the interest points. The feature points that fall 
%within this ellipse are then matched according to epipolar constraints.

In practice there are many situations where relying on the geometry of 
the image to filter correspondences is not possible, for example images 
without overlap, or adjacent objects in one image are that are separated 
in another.  Furthermore, methods using geometric constraints all 
require an initial set of correspondences. If this set of 
correspondences can be narrowed down to the most probable correct 
matches, the geometric matching algorithm will benefit in terms of speed 
and accuracy.  Finally some use cases might require a speed that simply 
cannot be achieved by complex geometric methods.

In the absence of geometric constraints, only few methods are available.  
As pointed out in \cite{szeliski2010}, the simplest approach to matching 
feature points is to return all matches above a given threshold of 
similarity.  This can be done with a fixed threshold or by finding the 
nearest neighbors for each point (still filtering by a threshold to 
avoid including matches for feature points that have no counterpart in 
the other image).  Lowe \cite{lowe2004sift} proposed the scale-invariant 
feature transform (SIFT) together with an alternative measure, where the 
uniqueness of a given match is found by looking at the two nearest 
neighbors of each feature point and calculating the matching score as 
the ratio of similarities.  Ranking the scores by their uniqueness and 
picking the $n$ best produces a set of correspondences that are 
distinctly matched across two images.
Of these three methods (fixed threshold, nearest neighbors, and 
\emph{SIFT}), \emph{SIFT} was found to perform best by a slight margin 
\cite{mikolajczyk2005performance}.

The two methods we propose in this paper are inspired by a simple but 
novel idea. If a given feature point in one image is better matched with 
other feature points from the \emph{same} image than points in the other 
image, then any matches from this feature point to points in the other 
image are considered unreliable and should be discarded.  This approach 
carries no implicit assumptions about the geometric consistency of 
matches and as such can easily be extended with other geometric 
solutions when appropriate or necessary.

Based on this idea,  we determine reliable matches as follows. 
\emph{Mirror Match (MM)} matches every feature from both images with all 
other features and filters matches based on the ratio of best to second 
best match as in \emph{SIFT}. \emph{Mirror Match with Clustering (MMC)} 
on the other hand takes the combined set of feature points from both 
images and clusters these points according to their descriptors.  If a 
resulting partition contains only feature points from one image, no 
matches are returned.  If the partition contains points from both 
images, \emph{Mirror Match} is used to find the best matches within this 
partition.  The experimental results show that both approaches generally 
outperform existing correspondence matching methods.

%Matching feature points against the entire set of points from both 
%images ensures that the distinctiveness of a returned correspondence is 
%higher. In almost all cases\footnote{Exceptions would include cases 
%where we want to find all particular points in a pattern and other use 
%cases where the correspondence isn't assumed to be unique}, a good 
%match between two images is unambiguous in the sense that there are no 
%other equally good potential matches to the same point.  This is the 
%key insight behind the algorithm presented by Lowe in 
%\cite{lowe2004sift}.  However the implication doesn't follow the other 
%way around. In the case that a feature point doesn't have a true 
%correspondence there might still exist point with which the feature 
%point is uniquely matched. The issue is particularly pronounced if we 
%compare two images that do not correspond. For any proposed 
%correspondence it is entirely probable that this correspondence is 
%unique even if it isn't correct. When we match against the feature 
%points of both images this ambiguity is avoided.  When the two images 
%have no overlap or objects in common, chances are that a feature point 
%will match better with another feature point from the same image in 
%which case it is easily discarded.
%
%Often images will contain repetitive patterns that are difficult to 
%match\footnote{In fact this particular problem has been given attention 
%before by for example \cite{fan2011towards}} because the feature 
%descriptors covering these patterns will be similar. If we remove points 
%that aren't deemed sufficiently unique like in \emph{MM} this means that 
%these points will often be discarded even if they are correctly matched.
%\emph{MMC} makes it possible to look at groups of similar feature points 
%one at a time and within each group find the best matches. This is done 
%by taking the set of feature points from both images and cluster them by 
%their similarity. In some cases the clustering will end up grouping 
%feature points of only one image together which can then easily be 
%discarded in the matching process.  In other cases partitions will 
%contain similar feature points from both images that can then be matched 
%using \emph{MM} but with much lower thresholds.
%

The paper is organized as follows.  Section~\ref{S:MatchingMethods} 
describes the proposed \emph{Mirror Match (MM)} and \emph{Mirror Match 
with Clustering (MMC)} algorithms.  Section~\ref{S:Experiments} presents 
the dataset used for evaluation and the experimental setup.  
Section~\ref{S:Results} discusses the benchmarking results obtained.  
Section~\ref{S:Summary} concludes the paper.

\section{Matching Methods}
\label{S:MatchingMethods}

\subsection{Mirror Match (\emph{MM})}

@@

\subsection{Mirror Match with Clustering (\emph{MMC})}
%
In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
non-geometric feature matching by clustering feature points by 
similarity. This process yields partitions of fairly similar feature 
points that we can match using the same approach as \emph{MM}.  
Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
%
%Before we introduce the implementation details we will go over the 
%problem of graph clustering and how it relates to feature matching.
%
%\subsubsection{Graph Clustering}
%
%Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
%\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
%function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
%points in an image and returns their matching score, we can define a 
%matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
%as the \emph{adjecency matrix} of the fully connected graph where each 
%vertex corresponds to a keypoint and the edge between two vertices has a 
%weight equal to the distance between the two corresponding keypoints.
%
%This representation reduces the problem of partitioning the keypoints 
%into groups to that of graph clustering or community structure depending 
%on the context. In the literature there are various ways of clustering a 
%graph according to different measures of what constitutes an optimal 
%partitioning. Traditionally the most used clustering algorithms have 
%been K-means and spectral clustering, but in recent years a host of new 
%algorithms have been proposed based on both Newman's concept of graph 
%modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
%\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
%well as information theoretical measures\footnote{See for example 
%\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
%in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
%new algorithms differ from K-means clustering and Spectral clustering 
%in that they do not require the number of expected to clusters to be 
%specified beforehand\footnote{Among the aforementioned methods, this is 
%true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
%tests done using randomly generated graphs with a known partitioning 
%\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
%markedly better than spectral clustering and 
%K-means\cite{lancichinetti2009}.
%
%The performance of clustering algorithms is a complicated issue, since 
%an optimal clustering given the same graph can vary depending on the 
%application. Spectral clustering for example will usually return a 
%partitioning where each partition is roughly equal in size\footnote{As 
%mentioned in \cite{von2007}} while the Louvain 
%clustering\cite{blondel2008} might return partitions of very uneven 
%size, even if the modularity measurement has been shown to penalize very 
%small clusters\cite{brandes2007}. Both behaviours can be beneficial 
%depending on the application, but when clustering feature points, 
%maintaining clusters of an even size usually means that some clusters 
%will be '\emph{catch-all}' clusters where the feature points that do 
%not fit anywhere else are grouped together. The necessity of specifying 
%the amount of partitions in for example Spectral clustering or Pott's 
%model clustering further exacerbates the issue since smaller partitions 
%are then combined into one to achieve the right amount of partitions.
%

@@

	%add desired spacing between images, e. g. ~, \quad, \qquad		  
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}{0.7\columnwidth}
		\includegraphics[width=\columnwidth]{images/MMC_graph_cropped}
		\caption{Cropped Section of Graph}
		\label{fig:cropped_graph}
	\end{subfigure}%
	\caption{The partitioned feature graph (a). Each vertex represents a 
		feature point; lines indicate high similarity between 
		points. A partition is a connected group with the same color. The border color of each node 
		indicates which image it belongs to.  Zooming into a section of the graph (b), the various cluster sizes can be seen, ranging from 
	hundreds of feature points to only two or three.}
	\label{fig:graph}
\end{figure}

@@

\section{Experiments}
\label{S:Experiments}
%
To reliably measure the accuracy of a matching method on real images, we 
either need a set of image pairs tied by a homography, or we have to manually count 
the number of inliers. The latter becomes prohibitive for large numbers of (non-trivial) images.

@@

%
%
%\subsection{Experimental setup}
We compare the \emph{MM} and \emph{MMC} algorithms to 
\emph{SIFT} \cite{lowe2004sift} as well 
as \emph{Isodata} \cite{das2008event}. 
\emph{Isodata} uses geometric constraints, whereas \emph{SIFT} does not.
%, which uses geometric information to improve the matching. 
%The comparison  with \emph{SIFT} serves to illustrate the relative performance of 
%\emph{MM} and \emph{MMC} to a state of the art algorithm without 
%geometric constraints. \emph{Isodata} is included to 
%illustrate the performance of an algorithm relying on geometric 
%constraints faced with image pairs that might not have any overlap.  
The 
comparison was done using the \emph{Murals} dataset (Figure~\ref{fig:murals}), the 
\emph{Graf} set (Figure~\ref{fig:Graf}) from \cite{mikolajczyk2005performance}, and two 
images %\footnote{100\_1942.jpg and 100\_1941.jpg} 
from the Gallagher dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).

@@

\section{Results}
\label{S:Results}

@@

@@

Given the versatility of the proposed algorithms, we are planning to apply them to problems that require high 
reliability faced with images that might not match, such as near 
duplicate detection or face recognition.
%
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\end{document}

>>>>

%\documentclass[report]{IEEEtran}
\documentclass{article}
\usepackage{footnote}
%\usepackage[font={small}]{caption}
\usepackage{sidecap}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
%\usepackage[stable]{footmisc}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\title{Reliable feature point matching}
\author{Jonas Arnfred}

\maketitle

\section{Introduction}
What is the subject of this thesis and in what part lies my 
contribution?
How is the report organized?

\section{Background}
Introduction to Computer Vision
 - Introduce common tasks that we are good at that computers aren't
 - Single in on tasks that we can solve using feature points

Introduction to feature points
 - Global explanation of what they are and how they serve to solve the 
problems mentioned before
 - How do we find them? (Examples making it intuitive why corners are 
nice)
 - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
 Scale, \ldots, Affine)
 - Introduce SIFT and explain how the different problems are tackled in 
SIFT)
 - Talk about other methods and how they are different

Matching feature points
 - What applications require matching?
 - How is matching usually done
 - Segue into related work from paper

\section{Matching feature points}
Basically c/p from paper, but better figures and maybe more explanations
 - Add path about graphs and how they are formed. Make sure to explain 
 the clustering in more detail and make it easier to understand
 - Add a good explanation for new figures and how the precision and 
 recall are calculated. This should appear somewhere before results.
 - Add part on spectral matching and modify accordingly. Make sure to 
 underline how the second plot shows how the geometric method is 
 independent of MMC and that they combined yield greater results.

\subsection{Proposed Matching Methods}
\label{S:MatchingMethods}

\subsubsection{Mirror Match (\emph{MM})}

@@

\subsubsection{Mirror Match with Clustering (\emph{MMC})}
%
In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
non-geometric feature matching by clustering feature points by 
similarity. This process yields partitions of fairly similar feature 
points that we can match using the same approach as \emph{MM}.  
Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
%
%Before we introduce the implementation details we will go over the 
%problem of graph clustering and how it relates to feature matching.
%
%\subsubsubsection{Graph Clustering}
%
%Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
%\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
%function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
%points in an image and returns their matching score, we can define a 
%matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
%as the \emph{adjecency matrix} of the fully connected graph where each 
%vertex corresponds to a keypoint and the edge between two vertices has a 
%weight equal to the distance between the two corresponding keypoints.
%
%This representation reduces the problem of partitioning the keypoints 
%into groups to that of graph clustering or community structure depending 
%on the context. In the literature there are various ways of clustering a 
%graph according to different measures of what constitutes an optimal 
%partitioning. Traditionally the most used clustering algorithms have 
%been K-means and spectral clustering, but in recent years a host of new 
%algorithms have been proposed based on both Newman's concept of graph 
%modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
%\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
%well as information theoretical measures\footnote{See for example 
%\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
%in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
%new algorithms differ from K-means clustering and Spectral clustering 
%in that they do not require the number of expected to clusters to be 
%specified beforehand\footnote{Among the aforementioned methods, this is 
%true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
%tests done using randomly generated graphs with a known partitioning 
%\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
%markedly better than spectral clustering and 
%K-means\cite{lancichinetti2009}.
%
%The performance of clustering algorithms is a complicated issue, since 
%an optimal clustering given the same graph can vary depending on the 
%application. Spectral clustering for example will usually return a 
%partitioning where each partition is roughly equal in size\footnote{As 
%mentioned in \cite{von2007}} while the Louvain 
%clustering\cite{blondel2008} might return partitions of very uneven 
%size, even if the modularity measurement has been shown to penalize very 
%small clusters\cite{brandes2007}. Both behaviours can be beneficial 
%depending on the application, but when clustering feature points, 
%maintaining clusters of an even size usually means that some clusters 
%will be '\emph{catch-all}' clusters where the feature points that do 
%not fit anywhere else are grouped together. The necessity of specifying 
%the amount of partitions in for example Spectral clustering or Pott's 
%model clustering further exacerbates the issue since smaller partitions 
%are then combined into one to achieve the right amount of partitions.
%

@@

	%add desired spacing between images, e. g. ~, \quad, \qquad		  
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}{0.7\columnwidth}
		\includegraphics[width=\columnwidth]{images/MMC_graph_cropped}
		\caption{Cropped subsection of Graph}
		\label{fig:cropped_graph}
	\end{subfigure}%
	\caption{The partitioned feature graph (a). Each vertex represents a 
		feature point; lines indicate high similarity between 
		points. A partition is a connected group with the same color. The border color of each node 
		indicates which image it belongs to.  Zooming into a subsection of the graph (b), the various cluster sizes can be seen, ranging from 
	hundreds of feature points to only two or three.}
	\label{fig:graph}
\end{figure}

@@

\subsection{Experiments}
\label{S:Experiments}
%
To reliably measure the accuracy of a matching method on real images, we 
either need a set of image pairs tied by a homography, or we have to manually count 
the number of inliers. The latter becomes prohibitive for large numbers of (non-trivial) images.

@@

%
%
%\subsubsection{Experimental setup}
We compare the \emph{MM} and \emph{MMC} algorithms to 
\emph{SIFT} \cite{lowe2004sift} as well 
as \emph{Isodata} \cite{das2008event}. 
\emph{Isodata} uses geometric constraints, whereas \emph{SIFT} does not.
%, which uses geometric information to improve the matching. 
%The comparison  with \emph{SIFT} serves to illustrate the relative performance of 
%\emph{MM} and \emph{MMC} to a state of the art algorithm without 
%geometric constraints. \emph{Isodata} is included to 
%illustrate the performance of an algorithm relying on geometric 
%constraints faced with image pairs that might not have any overlap.  
The 
comparison was done using the \emph{Murals} dataset (Figure~\ref{fig:murals}), the 
\emph{Graf} set (Figure~\ref{fig:Graf}) from \cite{mikolajczyk2005performance}, and two 
images %\footnote{100\_1942.jpg and 100\_1941.jpg} 
from the Gallagher dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).

@@

\subsection{Results}
\label{S:Results}

@@

\section{Applications}

\subsection{Panorama Recognition and Alignment}
One of the oldest practical problems approached in computer vision is 
the automatic stitching of several source images into a bigger image, 
such as panoramas and composite satellite photos\footnote{A brief 
overview of the history of image stitching can be found in Szeliski's 
book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
As part of the process of stitching together images, the individual 
images must be aligned and often transformed in perspective. Earlier 
methods relied on minimizing pixel dissimilarities in overlapping images 
while more recent methods have used local feature points to estimate the 
correct image alignment. Using local feature points carry the additional 
advantage that it is feasible to automatically recognize where each 
source image belong in the final panorama.

In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
image can be assembled by collecting the feature points of all source 
images and matching them to obtain a set of inter image matches.  By 
using \emph{RANSAC}\footnote{RANdom SAmple Consensus, an iterative 
    algorithm to estimate parameters from noisy data introduced in 
Fischler and Bolles in 1981 \cite{fischler1981ransac}} to find matches 
deemed as inliers between image pairs, they are able to recognize image 
neighbors and align them to construct the final panorama.

This process hinges on the effectiveness of the matching algorithm used 
to match the feature points. Not only is it important that true pairs 
are accurately matched, but since we are matching points in image pairs 
that might not be adjacent in the final panorama, we also need to make 
sure that we consistently reject false positives, i.e.\ proposed matches 
that link feature points which don't correspond.

To demonstrate the usefulness of \emph{MMC} applied to panorama 
recognition and alignment we construct a simple panorama stitcher taking
as input a set of $n$ source images $\left{I_0, \ldots, I_n\right}$ and 
returns as output a panoramic image stitched together from the source 
images. Based on the matches found by applying \emph{MMC} to $I$, the 
images are combined in an order corresponding to how many matches 
connect them, as done by Brown and Lowe \cite{brown2007automatic}.

Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
provides a way to globally optimize the accuracy of the image alignment} 
and a lot of image enhancements such as exposure adjustment and edge 
blurring to provide a seamless panorama. While these additions improve 
the end product, they don't influence the performance of panorama 
alignment and recognition and haven't been included in the simple 
comparison algorithm.

% About near duplicates mention how we can't use ransac to find inliers 
% since we can't necessarily construct a homography between two images

When we are performing panorama alignment and recognition with feature 
points, oth recognition and alignment of the source images is

There are two important steps to image stitching which i- Describe in 
general why better matching improves the results and speed on a broad 
range of different computer vision problems
 - Elaborate on why the two examples where chosen (are there any 
 particular reasons?)
 - Near duplicate detection
 - Panorama application

@@

Given the versatility of the proposed algorithms, we are planning to apply them to problems that require high 
reliability faced with images that might not match, such as near 
duplicate detection or face recognition.
%

\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\end{document}
